An automatic approach to find all possible calendar effects (periodic patterns) for an univariate time series

### 2021-02-21 paper/main.Rmd
computing threshold
changing normalisation section

---
title: Selecting and ranking interesting pairs of cyclic temporal granularities
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

@@

# The proposed distance measure

@@

```{r null4by2,fig.cap=" A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis. Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories. Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a). Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}

sim_varf_dist1 = function(nx, nfacet){
  rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}

@@

## Definition of the proposed distance measure

@@

From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances. Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:

@@

The maximum weighted pairwise distances are defined as:
$$WPD = max_{j, j', k, k'}(d*_{(jk), (j'k')})
\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.

@@

# Normalisation

The distribution of wpd is different for different levels of facets and x-axis levels. This is because the statistic maximum which is used to define wpd is affected by the number of categories. The measure would have higher values if $C_i$ or $C_j$ has higher levels. However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher. Therefore, in order to compare wpd across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure. Henceforth we call the measure already discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$. The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set. In the coming section, we have discussed two approaches to normalisation both through simulations.

## Simulation study

Most of the behavior of the measure wpd was studied via simulation. The simulations explore how wpd performs under various designs and parameters and its limitations. To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:

<!-- Numerous simulations were carried out in a wide range of scenarios. -->

<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->

- $nx$ (number of levels of x-axis)
- $nfacet$ (number of levels of facets)
- $\lambda$ (tuning parameter)
- $\omega$ (increment in each panel design)
- $dist$ (normal/non-normal distributions with different location and scale)
- $n$ (sample size for each combination of categories)
- $nsim$ (number of simulations)a
- $nperm$ (number of permutations of data)  
- $designs$  
$D_{null}$  (No difference in distribution)  
$D_{var_f}$ (Difference in distribution only across facets)  
$D_{var_x}$ (Difference in distribution only across x-axis)  
$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)

R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community. The nodes and the storage used are as follows:

@@

### Notations

Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{nfacet_{j}, j = 1, 2, \dots, nfacet\}$ be the set of x-axis and facet categories respectively. Each combination of $nx_{i}$ and $nfacet_{j}$is being referred to as a _panel_. Then the total number of panel is $nx*nfacet$. Let the total number of pairwise distances that could result in each panel be $\{z_k, k = 1, 2 , \dots, nx*nfacet\}$. Here, $\{z_1 = nx_1*nfacet_1\}$, $\{z_2 = nx_2*nfacet_2\}$ and $\{z_k = nx*nfacet\}$. Now, let $\{x_{k,l}, k = 1, 2, \dots, nx*nfacet, l = 1, 2, \dots, nsim\}$ denote the values of $wpd_{raw}$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation. Hence, for each of those $k$ panel, we have $nsim$ values of $wpd_{raw}$.

### Data generation

Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The value of $\lambda$ is set to $0.67$. $nsim = 200$, which means each of these scenarios are run $200$ times by permuting the data in each of the panels. And hence $200$ values of $wpd_{raw}$ are obtained for each of those 64 panels.

@@

The permutation approach ensures that the distribution of the normalised weighted pairwise distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$. Thus, the normalised distances is computed as follows: $x^{norm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{norm}_{k}$ is the value of the $wpd_{norm}$ for the $k^{th}$ panel.

While this works successfully to make the mean and standard deviation across different nx and nfacet (as seen in Figure \ref{fig:}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice. Hence, we propose another approach to normalisation which is more approximate than exact but still has the same accuracy when compared to the permutation approach.

@@

# Choosing harmonies with significant wpd

@@

# Application {#sec:application}

<!-- ## Smart meter data of Australia {#sec:smartmeter} -->

<!-- # how data looks -->

Clustering of electricity customers based on their consumption behavior facilitate effective market segmentation and hence better management and pricing.
Electricity demand time series are the primary source of information of customers' consumption behavior.
Due to technological developments, smart meters could provide large quantities of measurements on energy usage at more and more finer time intervals. Due to this extreme dimensionality along time of the demand data, it is a challenge to have clustering methods which could reduce the dimensionality to produce distinct clusters. One of the potential solutions is time series feature extraction. However, it is limited by the type of noisy, patchy and unequal time series that is very common in data sets of any residential customers. The idea is to choose similarity measures, which do not lose the core characteristic information of demand across different time deconstructions in aggregation processes and is robust against asynchronous or incomplete time series.

We use the data from one of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney. The data has customer wise data on energy consumption for every half hour from February 2012 to March 2014. <!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.--> The idea here is to
use our similarity measure and show improved cluster distinction as compared to baseline feature based approaches. A data set of 100 homes is used to evaluate both approaches. This is different to deterministic segmentation which attempts to characterise load as a function of a fixed number of parameters, such as occupancy or types of appliances, and use those parameters for classification. We only use their load patterns across time deconstructions to define the similarity measure.

<!-- Write about common load clustering methods -->

### Multidimensional scaling and cluster analysis

Cluster analysis and multidimensional scaling (MDS) methods are used to explore the temporal structure of various households, their interrelations and determine similar behaving clusters of households in this study.
MDS methods are used to produce a lower dimensional display space where each household is represented by a point and the distance between these points give the measure of similarity between these households. On the other hand, clustering techniques are used to provide information about the clustering structure of the households. Households that are in the same cluster can be considered to be more similar, while households are more dissimilar in their energy behavior across one or few temporal deconstructions.

$wpd_norm$ is considered as the measure of similarity or dissimilarity while using MDS and clustering techniques. $wpd_norm$ could be constructed for each pair of harmony for each household and then similarity could be measured across single or all harmonies together.

```{r mds}
set.seed(7777)
library(gravitas)
library(tsibble)
library(lubridate)
library(readr)

all_data <- read_rds(here("paper/sim_table/all_data.rds"))
sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds")) %>% 
  as_tsibble(index = reading_datetime,
             key = customer_id)

sm_unique_cust <- sm_cust_data %>% distinct(customer_id)

#sm_30 <- sample(sm_unique_cust$customer_id, 30)
sm_cust_samp <- sm_cust_data %>% 
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  filter(year(reading_datetime) == 2012)  %>% 
  create_gran("day_week") %>% 
  create_gran("hour_day")

#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")

facet_variable = "day_week"
x_variable = "hour_day"

one_harmony_data <- all_data %>%
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  filter(facet_variable == "day_week",
                    x_variable == "hour_day") %>% 
  mutate(customer_id = as.character(customer_id))

mds<- one_harmony_data %>%
  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
  dist() %>%          
  cmdscale() %>%
  as_tibble()

colnames(mds) <- c("Dim.1", "Dim.2")
rownames(mds) <- unique(one_harmony_data$customer_id)
mds <- mds %>%
  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
  select((customer_id)
         , Dim.1, Dim.2)
```

```{r clustering}
# K-means clustering
clust <- kmeans(mds, 3)$cluster %>%
  as.factor()
mds <- mds %>%
  mutate(groups = clust)

# Plot and color by groups
ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          label = rownames(mds),
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE)

@@

# check transformation and scalar approaches are same

```{r scalar-approach}
set.seed(7777)
all_data <- read_rds("paper/sim_table/all_data_scalar.rds")
sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
set.seed(7777)
sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
sm_cust_samp <- sm_cust_data %>% 
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
  as_tsibble(index = reading_datetime,
             key = customer_id) %>% 
  create_gran("day_week") %>% 
  create_gran("hour_day")

#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")

facet_variable = "day_week"
x_variable = "hour_day"

one_harmony_data <- all_data %>%
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  filter(facet_variable == "day_week",
         x_variable == "hour_day") %>% 
  mutate(customer_id = as.character(customer_id))

mds<- one_harmony_data %>%
  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
  dist() %>%          
  cmdscale() %>%
  as_tibble()

colnames(mds) <- c("Dim.1", "Dim.2")
rownames(mds) <- unique(one_harmony_data$customer_id)
mds <- mds %>%
  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
  select((customer_id)
         , Dim.1, Dim.2)

ggpubr::ggscatter(mds,
                  x = "Dim.1",
                  y = "Dim.2", 
                  label = rownames(mds),
                  size = 1,
                  repel = TRUE)

# clustering as well

d = one_harmony_data %>%
  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
  dist()

hc = stats::hclust(d,method="complete")
plot(hc)
groups<-cutree(hc, k=4)

all_data_cluster <- cbind(one_harmony_data, groups) %>% 
  left_join(mds, by = "customer_id") %>% 
  mutate(groups = as.factor(groups))

ggpubr::ggscatter(all_data_cluster,
                  x = "Dim.1",
                  y = "Dim.2", 
                  label = rownames(mds),
                  color = "groups",
                  size = 1,
                  repel = TRUE)

10018272 is a customer from cluster 3, for which hour_day/wknd-wday comes after wknd-wday/day-month as opposed to 10006414 (cluster 1) for whom the direction is reversed.

10006414

all_data %>% 
  filter(customer_id ==  10006414) %>% 
  arrange(-wpd_norm)

sm_cust_data %>% 
  filter(customer_id ==  10006414) %>% 
  prob_plot("hour_day",
            "wknd_wday",
            plot_type = "quantile",
            quantile_prob = c(0.5),
            symmetric = FALSE,
            response = "general_supply_kwh")

sm_cust_data %>% 
  filter(customer_id ==  10006414) %>% 
  prob_plot("hour_day",
            "day_week",
            plot_type = "quantile",
            quantile_prob = c(0.5),
            symmetric = FALSE,
            response = "general_supply_kwh")

all_data %>% 
  filter(customer_id ==  10007340) %>% 
  arrange(-wpd_norm)

sm_cust_data %>% 
  filter(customer_id ==  10007340) %>% 
  prob_plot("day_month",
            "day_week",
            plot_type = "quantile",
            quantile_prob = c(0.5),
            symmetric = FALSE,
            response = "general_supply_kwh")

sm_cust_data %>% 
  filter(customer_id ==  10007340) %>% 
  prob_plot("hour_day",
            "day_month",
            plot_type = "quantile",
            quantile_prob = c(0.5),
            symmetric = FALSE,
            response = "general_supply_kwh")

all_data %>% 
  filter(customer_id ==  10018272) %>% 
  arrange(-wpd_norm)

```{r}
raw_data <- sm_cust_data %>% 
  left_join(mds, by = "customer_id")

p1 <- raw_data %>% 
  filter(groups==1) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  )

p2 <- raw_data %>% 
  filter(groups==2) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  )

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  )
library(patchwork)
p1/p2/p3

```{r}
raw_data <- sm_cust_data %>% 
  left_join(mds, by = "customer_id")

p1 <- raw_data %>% 
  filter(groups==1) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)

p2 <- raw_data %>% 
  filter(groups==2) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)
library(patchwork)
p1
p2
p3

```{r hour-day-day-month, eval = FALSE}

set.seed(7777)
library(gravitas)
library(tsibble)
library(lubridate)
library(readr)

all_data <- read_rds("sim_table/all_data.rds")
sm_cust_data <- read_rds("data/sm_cust_data.rds")
sm_unique_cust <- sm_cust_data %>% distinct(customer_id)

#sm_30 <- sample(sm_unique_cust$customer_id, 30)
sm_cust_samp <- sm_cust_data %>% 
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  filter(year(reading_datetime) == 2012) %>% #for demo just show one column
  as_tsibble(index = reading_datetime,
             key = customer_id) %>% 
  create_gran("wknd_wday") %>% 
  create_gran("week_month")

#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")

facet_variable = "wknd_wday"
x_variable = "week_month"

one_harmony_data <- all_data %>%
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  filter(facet_variable == "wknd_wday",
                    x_variable == "week_month") %>% 
  mutate(customer_id = as.character(customer_id))

mds<- one_harmony_data %>%
  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
  dist() %>%          
  cmdscale() %>%
  as_tibble()

colnames(mds) <- c("Dim.1", "Dim.2")
rownames(mds) <- unique(one_harmony_data$customer_id)
mds <- mds %>%
  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
  select((customer_id)
         , Dim.1, Dim.2)

clust <- kmeans(mds, 3)$cluster %>%
  as.factor()
mds <- mds %>%
  mutate(groups = clust)

# Plot and color by groups
ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          label = rownames(mds),
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE)

### Advantage over taditional feature based methods

Since probability distribution of the load is considered across different cyclic granularity, there is no discarding of valuable data that might result from bringing all customers to the same time horizon.
Moreover, since our metric is based on probability distribution, it will not be sensitive to outlier days and hence the clustering process will not be biased.
Moreover, feature extraction applies to all days for all customers at once and therefore does not support parallel computing. Our metric is computed for each household separately and can even run for each each harmonies separately and thus fits well into the parallel computing framework.

### Write the method in notations

-  notation of time series for each customer
-  wpd
-  harmonies
-  cluster

### Distinction, repeatability, and robustness metrics

### Putting similar households on linear scale

>>>>

---
title: An automatic approach to find all possible calendar effects (periodic patterns) for an univariate time series
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

@@

# The distance measure for quantifying patterns in harmonies

@@

```{r null4by2,fig.cap=" A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis. Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories. Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a). Display d is most interesting as distribution of the rv changes across both facet and x-axis variable.", eval = FALSE}

# sim_varf_dist1 = function(nx, nfacet){
#   rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}

@@

## Definition of the distance measure

@@

From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances. Hence, for a suitable tuning parameter $0<\lambda<1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:

@@

The maximum weighted pairwise distances are defined as:
$$wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')})
\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.

@@

## Properties of the distance measure

A simulation study is carried out to explore how $wpd$ performs under various designs, its parameters and limitations. To this end, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of $wpd$:

- $nx$ (number of levels of x-axis)
- $nfacet$ (number of levels of facets)
- $\lambda$ (tuning parameter)
- $\omega$ (increment in each panel design)
- $dist$ (normal/non-normal distributions with different location and scale)
- $n$ (sample size for each combination of categories)
- $nsim$ (number of simulations)
- $nperm$ (number of permutations of data)  
- $designs$  
$D_{null}$  (No difference in distribution)  
$D_{var_f}$ (Difference in distribution only across facets)  
$D_{var_x}$ (Difference in distribution only across x-axis)  
$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)

Results are presented in two parts. The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section. The rest of the results that discusses the relationship of the $wpd$ with other factors is presented in the Supplementary section of the paper.

### Design of the simulation study

Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. Each combination is being referred to as a _panel_. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The values of $\lambda$ is set to $0.67$ and values of raw wpd $wpd$ is obtained. This entire design applies to the null cases and hence there is no difference in distribution between any categories in the panel.

### Results

Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different nx and nfacet categories. Both shape and scale of the distributions change across panels. This is not desirable as it would mean we would not be able to compare $wpd$ across different $nx$ and $nfacet$ as each of them are drawn from distributions with different locations and scale. In Figure \ref{fig:quadratic}, we see how the median of $wpd_{raw}$ varies with the total number of distances $nx*nfacet$ for each panel. The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.

```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")

G21 %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("raw wpd")
```

```{r quadratic, fig.cap = "$wpd_{raw}$ is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
G21 %>% 
  ggplot(aes(x=nx*nfacet, y = value)) +
  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")

# Normalisation of the distance measure

The distribution of wpd is different for different levels of facets and x-axis levels. This is because the statistic maximum which is used to define $wpd$ is affected by the number of categories. The measure would have higher values if $A$ or $B$ has higher levels. However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high. Therefore, in order to compare $wpd$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure. Henceforth we call the measure already discussed as $wpd_{raw}$ and the normalized measure as $wpd_{norm}$. The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set. We discuss two approaches for normalization, both of which are based on the simulation results conducted in the earlier section.

<!-- The nodes and the storage used are as follows: -->

@@

We need a transformation on ${wpd}$ which will make it independent of the values of $nx*nfacet$. Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar across different $nx$ and $nfacet$.

<!-- ### Notations -->

<!-- Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{nfacet_{j}, j = 1, 2, \dots, nfacet\}$ be the set of x-axis and facet categories respectively. Each combination of $nx_{i}$ and $nfacet_{j}$is being referred to as a _panel_. Then the total number of panel is $nx*nfacet$. Let the total number of pairwise distances that could result in each panel be $\{z_k, k = 1, 2 , \dots, nx*nfacet\}$. Here, $\{z_1 = nx_1*nfacet_1\}$, $\{z_2 = nx_2*nfacet_2\}$ and $\{z_k = nx*nfacet\}$. Now, let $\{x_{k,l}, k = 1, 2, \dots, nx*nfacet, l = 1, 2, \dots, nsim\}$ denote the values of $wpd_{raw}$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation. Hence, for each of those $k$ panel, we have $nsim$ values of $wpd_{raw}$. -->

@@

The permutation approach ensures that the distribution of the normalized distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$. The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm$ for the $k^{th}$ panel. Standardizing the variable $wpd_{perm}$ in this approach leads to $location = 0$ and $scale = 1$ for this variable.

While this works successfully to make the mean and standard deviation across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice. Hence, we propose another approach to normalization which is more approximate than exact but still has the same accuracy when compared to the permutation approach.

*incorporate from the document combining_normalisation_method.Rmd*

@@

Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches. R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.

# Ranking and selecting significant harmonies

@@

# Application in residential smart meter data {#sec:application}

```{r household2and4}
id2_tsibble <- elec %>% 
   filter(id == 2) %>% 
   as_tsibble(index = date_time)

harmonies2 <- id2_tsibble %>%
  harmony(
    ugran = "month",
    filter_in = "wknd_wday",
    filter_out = c("hhour", "fortnight")
  )

harmonies4 <- id4_tsibble %>%
  harmony(
    ugran = "month",
    filter_in = "wknd_wday",
    filter_out = c("hhour", "fortnight")
  )

library(tictoc)
tic()

all_harmony2 <- hakear::select_harmonies(id2_tsibble,
   harmony_tbl = harmonies2,
   response = kwh,
   nperm = 200,
   nsamp = 200
 )

toc()

library(tictoc)
tic()
all_harmony4 <- hakear::select_harmonies(id2_tsibble,
   harmony_tbl = harmonies2,
   response = kwh,
   nperm = 200,
   nsamp = 20
 )
toc()

@@
